Create year end summaries

### 2024-03-04 src/year-end-summary.Rmd
Added finding-examples to 23

```{r}
# Put it all together
yyyy_list <- c(1999:2024)
n_files <- 0
for (yyyy in yyyy_list) {
  yy <- str_sub(yyyy, 3, 4)
  output_file <- glue("../text/{yy}/{yyyy}.md")
  glue("../text/{yy}") %>%
    list.files %>%
    str_subset("md$") -> f
  source_files <- NULL
  date_list <- NULL
  n_lines <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{yy}/{fn}"))
    source_files %<>% append(check_source(file_text))
    date_list %<>% append(check_date(file_text))
    n_lines %<>% append(length(file_text))
  }

>>>>

```{r}
# Put it all together
yyyy_list <- c(2023:2023)
n_files <- 0
for (yyyy in yyyy_list) {
  yy <- str_sub(yyyy, 3, 4)
  output_file <- glue("../text/{yy}/{yyyy}.md")
  glue("../text/{yy}") %>%
    list.files %>%
    str_subset("md$") -> f
  source_files <- NULL
  date_list <- NULL
  n_lines <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{yy}/{fn}"))
    source_files %<>% append(check_source(file_text))
    date_list %<>% append(check_date(file_text))
    n_lines %<>% append(length(file_text))
  }
